### 2021-07-15 doc/thesis/chapters/implementation.tex
section comments
testbench

This chapter describes the most important details of each implementation variant.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Transmitter}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pre-Emphasis and De-Emphasis}
TODO: show effects in spectrum, show how to design the filters

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fixed Point Arithmetic}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Receiver}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Analysis}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{External Hardware}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{System Level Integration for Verification}

@@

\section{VHDL (no shortcut)}
  \subsection{Testbench}
  \subsection{Channel Selection (IF to Channel-BB)}
  \subsection{Phase Detector}
  \subsection{other Elements}

  \section{High-Level Synthesis}
  \subsection{Testbench}
  \subsection{Channel Selection (IF to Channel-BB)}
  \subsection{Phase Detector}
  \subsection{other Elements}

\section{Common Testbench}
  \subsection{Architecture (same tb for VHDL and HLS-generated HDL)}
  \subsection{Framework cocotb, with ghdl compiler}
  Instantiate both HDL models in the testbench.\\
  Display a direct comparison of outputs in graphs. This is practical, since the cocotb framework runs in python and graphs can be generated using Python's matplotlib.

>>>>

This chapter describes the most important details of each implementation variant.
The implementation variants in High-Level Synthesis and VHDL are highlighted especially, since they are the main focus of this thesis.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Transmitter}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pre-Emphasis and De-Emphasis}
TODO: show effects in spectrum, show how to design the filters

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fixed Point Arithmetic}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Receiver}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Analysis}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{External Hardware}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{System Level Integration for Verification}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{VHDL (TODO: no shortcut?)}

In this section, the most important details of the VHDL implementation are described.
This implementation variant is one of the two major implementation focus points of this thesis.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Testbench}

In the development of software that runs on a CPU, the tool of step-by-step debugging is commonly used during the development process.
Various verification and testing libraries exist, in order to create unit tests, for example.
The advantage is, that the code that is developed there, can be compiled and run on the target CPU directly, while maintaining the direct step-by-step representation of the code.

However, in the development of hardware with any hardware description language (HDL), this is not possible.
HDL languages provide a syntax and semantic representation that allow to create parallel structures and a dependency on timing, such as a system clock.
Before this code can be run on the target hardware, i.e. an FPGA, it needs to run through a process called synthesis.
In synthesis, the HDL code is translated into a netlist and is consequently mapped into hardware logic cells that are available in the target device.
Various optimizations are done during this process, so that the direct connection to the code representation is lost.
Additionally, it is impossible to access every single signal within the design during debugging on the hardware, which probably is one of the main issues.
Synthesis tools like Xilinx Vivado provide support to make debugging possible in hardware, but require a large effort to implement them.
Another big factor that speaks against debugging in hardware, is that the process of synthesis takes a comparably large amount of time to transform code into the target technology.
Each time the code is adapted, the entire synthesis process needs to be started over.

Because of all these reasons, debugging HDL code step-by-step as in software is not possible.\\

Thus, in order to allow debugging and verification of HDL code, the technology of simulation was invented.
Here, the HDL is also translated into a netlist that represents all the parallel processes just as in hardware, but the subsequent step of synthesis is not taken.
Therefore, simulation comes to a result much faster.
Since HDL designs actually only consist of electrical wires and some blocks (todo richtiges wort?), it is difficult to verify correct values.
The testbench environment is a very important factor in any project that includes hardware description language (HDL) code.
The reason therefor is that debugging

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Channel Selection (IF to Channel-BB)}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Phase Detector}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{other Elements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{High-Level Synthesis}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Testbench}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Channel Selection (IF to Channel-BB)}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Phase Detector}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{other Elements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Common Testbench}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Architecture (same tb for VHDL and HLS-generated HDL)}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Framework cocotb, with ghdl compiler}
  Instantiate both HDL models in the testbench.\\
  Display a direct comparison of outputs in graphs. This is practical, since the cocotb framework runs in python and graphs can be generated using Python's matplotlib.
